On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-19 Manuscript/manuscript.tex
Small Format Changes

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite
sample is required for block bootstrap confidence intervals to work well. This
study aims to answer this question in a simple simulation setting where the data
are generated from a first-order autoregressive process. The empirical coverage
rates of several commonly used bootstrap confidence intervals for the mean,
standard deviation, and the lag-1 autocorrelation coefficient are compared.
A quite large sample is found necessary for the intervals to have the right
coverage rates even when estimaiting a simple parameter like the mean. Some
block bootstrap methods could fail when estimating the lag-1 autocorrelation.
It is surprising that the coverage property even deteriorates as the sample size
increases with some commonly used block bootstrap confidence intervals including
the percentile intervals and Bias-Corrected intervals.

@@

Block bootstrap is a powerful tool for constructing confidence intervals (CI)
when making inferences about dependent data. Early ideas were developed
independently by \citet{hall1985resampling, carlstein1986use, kunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is particularly useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows to infinity. However,
when dealing with finite sample sizes, an important question is how large the
sample size needs to be for block bootstrap CIs to have the
desired coverage rates.

\jy{too wordy; do some condensing}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate even as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size of 100 and the correlation coefficientis equivalent to 0.
The general consensus is that a big sample size is necessary.

@@

The remainder of the paper is organized as follows.
Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
bootstrap estimates to construct CIs; a simple CI obtained by recentering at the
point estimate is proposed for comparison. Section~\ref{sec:simu} reports a
simulation
study comparing the coverage rates of six???block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

\jy{Practice my writing style guidelines. Use two blank lines to separate
  paragraphs.}

@@

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the rate of change of of the standard error of $\hat\theta_n$ with respect
to~$\theta$.

@@

For estimating~$\mu$,
Student's $t$ CIs appear to have the highest coverage rates with respect 
to estimating~$\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
furthest.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
$\phi$ observed, although there is no trend of coverage deterioration, 
indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
the nominal rate.
The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard CIs are used, and $n \geq 400$ is fine is
Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
for other CIs. For $\phi = 0.2$, 
comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
larger sample size appears to be necessary. Student's $t$ CIs are the closest to
$95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:phi}, 
Percentile, %CBP, %
$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3200$, indicating that 
perhaps a larger $n$ is needed if these CIs are used. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
comfortably at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma_x$,
$BC_a$ should not be used, and Student's $t$ again has the highest
\eds{highest?} \mc{addressed} coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method Bootstrap CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper bounds
    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $\bar\theta_n^{(b)}$ (red). }
  \label{fig:npi}
\end{figure}

@@

Block bootstrap is a useful method for estimating parameters of a time
series, from simple parameters like the mean to more complicated temporal
 dependence factors.
%The motivation for the study is the idea that block bootstrap procedure will
%perfectly estimate a parameter of a time series given an infinitely large
%sample. The goal for this study was to find what is a good enough finite
%sample length for block bootstrap estimation to recover the parameter of a
%time series at an acceptable rate.
 We know theoretically that the block bootstrap procedure will cover
  parameter of a time series at the nominal level given an
 infinitely large
sample, so the goal for this study was to find the smallest finite
sample length $n$ of a time series in order for the block bootstrap procedure
to 
recover its associated parameters at an acceptable rate.

Again, this analysis relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, 
whereas Percentile, 
%CBP, 
$BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct the 
bias, but the width of the CI seems to be inconsistent. The acceleration 
factor of the $BC_a$ CI seems to fail, as the width of the CI
seems to be inconsistent.

When using Student's $t$ intervals and $\phi$ is
unknown, the results of this study suggest that an $n > 3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

>>>>

\begin{abstract}
Block bootstrap is widely used in constructing confidence intervals for
parameters estimated from stationary time series. Theoretically, the method
should provide valid confidence intervals as the length of the time series goes
to infinity. In practice, however, it is necessary to know how large of a finite
sample is required for block bootstrap confidence intervals to work well. This
study aims to answer this question in a simple simulation setting where the data
are generated from a first-order autoregressive process. The empirical coverage
rates of several commonly used bootstrap confidence intervals for the mean,
standard deviation, and the lag-1 autocorrelation coefficient are compared.
A quite large sample is found necessary for the intervals to have the right
coverage rates even when estimating a simple parameter like the mean. Some
block bootstrap methods could fail when estimating the lag-1 autocorrelation.
It is surprising that the coverage property even deteriorates as the sample size
increases with some commonly used block bootstrap confidence intervals
including the percentile intervals and Bias-Corrected intervals.

@@

Block bootstrap is a powerful tool for constructing confidence intervals (CI)
when making inferences about dependent data. Early ideas were developed
independently by 
\citet{hall1985resampling, carlstein1986use,ckunsch1989jackknife}.
It has since been applied in various fields such as econometrics
\citep{mackinnon2006bootstrap} and meteorology \citep{varga2017generalised}.
Block bootstrap is particularly useful for serially dependent
data when the serial dependence is not specified or not of primary interest.
The method is expected to produce CIs with coverage rates
matching their nominal levels as the sample size grows to infinity. However,
when dealing with finite sample sizes, an important question is how large the
sample size needs to be for block bootstrap CIs to have the
desired coverage rates.

\jy{too wordy; do some condensing}
The performance of bootstrap standard errors with independent data
in providing valid uncertainty measures has been extensively studied.
For example, for non-block bootstrap, \citet{hesterberg2015teachers} notes
that while percentile-based CIs for the mean from nonparametric bootstrap
are more accurate than $t$-intervals for larger sample sizes, they are
less accurate for smaller sample sizes. \citet{chernick2009revisiting} finds 
that the best choice of method for estimating
the parameter of a distribution is dependent on the sample size, the number of
bootstrap resamples, and the confidence level. In the context of structural
equation modeling, \citet{nevitt2001performance} find
that a sample size of 200--1000 is usually sufficient for interval estimation
using standard nonparametric bootstrap. In estimating the proportion of 
variation attributable to certain variable, \citet{burch2012nonparametric} finds
that three nonparametric bootstrap methods (standard, percentile, and 
bias-corrected
and accelerated) approach the coverage of a pivotal quantity as the sample size
gets larger for an underlying normal distribution, but for other distributions, 
coverage may deteriorate even as the sample size increases.
When attempting to create interval estimations for the Pearson correlation 
coefficient of bivariate normal data, \citet{puth2015variety} find bootstrap 
methods to be less accurate than the Fisher's transformation method even 
for a sample of size of 100 and the correlation coefficient is equivalent to 0.
The general consensus is that a big sample size is necessary.

@@

The remainder of the paper is organized as follows.
Section~\ref{sec:bbci} reviews block bootstrap procedures and how to use block
bootstrap estimates to construct CIs; a simple CI obtained by recentering at the
point estimate is proposed for comparison. Section~\ref{sec:simu} reports a
simulation
study comparing the coverage rates of six block bootstrap CIs. A discussion
concludes in Section~\ref{sec:disc}.

@@

\jy{Practice my writing style guidelines. Use two blank lines to separate
  paragraphs.} \mc{addressed}

@@

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}.
\]
Define
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right)
\text{ and }
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of the standard error of $\hat\theta_n$ with respect to
$\theta$.

@@

Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
be the best method for estimating $\mu$.
For $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
nominal rate for all $n$ observed. For 
$\phi = -0.2$, 
all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n \geq 200$ seems to 
be large enough to recover $\mu$ at the nominal rate when using any CIs
 besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
  all $n$.
For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
 rate for all $n \geq 200$.
For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
 rate for all $n \geq 800$.

Based on Figure~\ref{fig:sigma}, Student's $t$ also seems to generally
be the best method for estimating $\sigma$.
for $\phi = -0.4$, $n \geq 1600$ is sufficient to recover $\sigma$
at the nominal level when using
any CIs besides Standard CIs, which seem to recover $\sigma$ at the nominal 
rate for all $n \geq 800$, and Student's $t$ CIs, which seem to recover $\sigma$
at the nominal rate for all $n \geq 400$. For $\phi = -0.2$, $n \geq 200$ is 
adequate to recover $\sigma$ at the nominal rate with Student $t$ CIs, 
but other CIs seem to require $n \geq 800$. For $\phi = 0$, or when the sample
is independently normally distributed, $n \geq 400$ seems to be about enough
to recover $\sigma$ for all CIs, but Student's $t$ CIs can recover $\sigma$ for
$n \geq 100$. For $\phi = 0.2$, $n \geq 800$ is adequate for CIs besides the
Student's $t$ CI, which recovers $\sigma$ well for $n \geq 200$. For 
$\phi  = 0.4$, $n \geq 1600$ seems necessary for CIs other that Student's $t$ 
CIs, which recover $\sigma$ at the nominal level for $n \geq 400$.

Based on Figure~\ref{fig:phi}, Student's $t$ again seems to generally
be the best method for estimating $\phi$. For high absolute values of $\phi$, 
Percentile, $BC$, and $BC_a$ CIs
deteriorate in coverage as $n$ increases. For $\phi = -0.4$, Standard, Student's
$t$, and Proposed CIs recover $\phi$ for $n \geq 100$. For $\phi = -0.2$, 
Standard and Proposed CIs recover $\phi$ at the nominal rate for $n \geq 200$, 
whereas this can be done for $n \geq 100$ with Student's $t$ CIs. For $\phi = 
0$, or when the sample
is independently normally distributed, Standard and Proposed CIs recover 
$\phi$ at the nominal level  for $n \geq 400$, and this is achievable for 
$n \geq 100$ with Student's $t$ CIs. For $\phi = 0.2$ and $\phi = 0.4$, Standard 
and Proposed CIs recover $\phi$ for $n \geq 200$, and Student's $t$ CIs 
recover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest
 coverage
overall, although that leads to over-coverage for small sample sizes when $\phi$
 is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI recover $\mu$ 
very close to the nominal rate even for small sample sizes. For positive $\phi$, a
larger sample size appears to be necessary regardless of the CI used. In the
case that $\phi$ is unknown and expected to be greater than $0$, $n > 800$
may be
necessary for block bootstrap interval estimation of $\mu$ when using the
Student's $t$ CI. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma_x$,
Student's $t$ again has the highest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 400$ may be necessary for block bootstrap interval estimation of
$\sigma_x$ when using the Student's $t$ CI. Again, if $\phi$ is known, a lesser
sample size may be enough.
When estimating $\phi$, Percentile, $BC$, and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix
the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 100$ is certainly large enough to
recover $\phi$ when using the Student's $t$ method.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/norm_phi_intervals}
  \caption{100 replicate Percentile, Bias-Corrected, and Proposed Method
  Bootstrap CIs for samples of $n = 800$ for
    an AR(1) process with $\phi = 0.4$. For each replicate, the lower and upper
    bounds
    of the CIs are displayed, as well as $\hat\theta_n$ (blue) and $
    \bar\theta_n^{(b)}$ (red). }
  \label{fig:npi}
\end{figure}

@@

Block bootstrap is a useful method for estimating parameters of a time
series, from simple parameters like the mean to more complicated temporal
 dependence factors.
 We know theoretically that the block bootstrap procedure will cover
  parameter of a time series at the nominal level given an
 infinitely large
sample, so the goal for this study was to find the smallest finite
sample length $n$ of a time series in order for the block bootstrap procedure
to 
recover its associated parameters at an acceptable rate.

Again, this analysis relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the five types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for Standard, Student's $t$, and Proposed Method CIs, 
whereas Percentile, 
$BC$, and $BC_a$ intervals exhibited coverage deterioration as $n$
increased. The Percentile CI's coverage deterioration can be attributed to
bias that is not corrected as $n$ increases. Specifically, as $n$ increases, 
the width of the CI decreases, but because the Percentile CI
underestimates $\phi$, the coverage decreases. The $BC$ CI seems to correct
the 
bias, but the width of the CI seems to be inconsistent. The acceleration 
factor of the $BC_a$ CI seems to fail, as the width of the CI
seems to be inconsistent.

When using Student's $t$ intervals and $\phi$ is
unknown, the results of this study suggest that an $n \geq 800$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$ when using smaller
sample sizes, 
meaning that if $\phi$ is known to have a very negative value, another CI
may be required.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, $n \geq 100$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
